---
title: "LobsterReport"
author: "Anna PerezWelter and Jamie K. Miller"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
### Install Packages

library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(pwr)
library(effsize)
library(ggplot2)
library(tidyr) # This package is to convert to tidy format with spread() function.
library(vcdExtra) # Perhaps this one will do it.
library(dplyr) # For summary stats?
library(sjstats) # For chi-square
library(ggsignif) # To add significance brackets
library(xtable) # For ANOVA table
library(RColorBrewer)
```

```{r, message=FALSE, include = FALSE}
### Read in Data and Data Source

size <- read_csv("lobster_size_abundance.csv")

# Loaded 3265 obs of 8 variables.

traps <- read_csv("lobster_traps.csv")

# Loaded 5741 obs of 10 variables.

###############################

# Data Source: Reed, D. . 2017. SBC LTER: Reef: Abundance, size and fishing effort for California
# Spiny Lobster (Panulirus interruptus), ongoing since 2012. Santa Barbara Coastal Long Term Ecological
# Research Project. doi:10.6073/pasta/81ce20b29614ec99d85d54907eaa3e8e

```

```{r, message = FALSE, include = FALSE}
# Preliminary Data Exploration: Lobster counts at all five locations from 2012 to 2017. 

### Lobster Abundance Data Formating

# Filter to exclude rows where the lobster count was zero. Only show columns year, site, size, and count.

size_tidy <- size %>%
  select(YEAR, SITE, SIZE, COUNT) %>%
  filter(COUNT != 0)

# Loaded 2878 obs of 4 variables.

######################

# Convert file 'size' to tidy format

size_tidier <- size_tidy %>%
  as.data.frame() %>%
  expand.dft(freq = "COUNT")

# Loaded 4554 obs of 3 variables.

# Lobster carapace length and counts are now in tidy format. Use 'size_tidier'.

size_tidier
```

### 1. Lobster abundance and fishing pressure (2012-2017)
```{r, echo = FALSE}
# Data Exploration: Lobster counts at all five locations from 2012 to 2017. 

### 1. Lobster abundance and fishing pressure (2012-2017)

# 1a. Summarize  trap data in a table grouped by Year and Site, filtered by 5 sites.
# Trap abundance bar graph to show fishing pressure per year at each site.

traps_summary <- traps %>%
  select(YEAR, SITE, TRAPS) %>%
  filter(SITE == "AQUE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "IVEE" | SITE == "CARP") %>%
  group_by(YEAR, SITE) %>%
  summarize(count = length(TRAPS))

# Loaded 30 obs of 3 variables summary table.

trap_graph <- ggplot(traps_summary, aes(x = YEAR, y = count)) +
                       geom_bar(position = position_dodge(), stat = "identity") +
                       facet_wrap(~SITE) +
  theme_classic()
trap_graph

```

```{r, echo = FALSE}
### 1. Lobster abundance and fishing pressure (2012-2017)

# 1b. Summarize lobster data in a table grouped by Year and Site, filtered by 5 sites.
# Lobster abundance bar graph

lobster_summary <- size_tidier %>%
  filter(SITE == "AQUE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "IVEE" | SITE == "CARP") %>%
  group_by(YEAR, SITE) %>%
  summarize(count = length(SIZE))

lobster_graph <- ggplot(lobster_summary, aes(x = YEAR, y = count)) +
                      geom_bar(position = position_dodge(), stat = "identity") +
                      facet_wrap(~SITE, scale = "free") +
  theme_classic()
lobster_graph
```

```{r}
### 1. Lobster abundance and fishing pressure (2012-2017)
# Second attempt at useful graph

trap_graph_2 <- ggplot(traps_summary, aes(x = YEAR, y = count)) +
                       geom_bar(position = position_dodge(), stat = "identity", aes(fill = SITE)) +
  theme_classic()
trap_graph_2


lobster_graph_2 <- ggplot(lobster_summary, aes(x = YEAR, y = count)) +
                      geom_bar(position = position_dodge(), 
                               stat = "identity", aes(fill = SITE)) + 
                               scale_fill_brewer(~SITE, palette = "terrain_hcl(5, c=c(65,0), l=c(45,95), power=c(1/3,1.5))") +
  theme_classic()
lobster_graph_2


```




### 2. Compare mean lobster size across five sites in 2017
```{r, include = FALSE}
### 2. Compare mean lobster size across five sites in 2017
# Summary Statistics
# Tests for normality
# Hypothesis Test

#####################################
# Summary Statistics
# Create a summary table, grouped by site, that includes median, maximum, mean, sd, and sample size values.
# Round values to 2 decimal points.

summary_stats_size_2017 <- size_tidier %>%
  filter(YEAR == 2017) %>%  
  group_by(SITE) %>%
  summarize(median = round(median(SIZE),2), 
            max = max(SIZE),
            mean = round(mean(SIZE),1),
            sd = round(sd(SIZE),1),
            n = length(SIZE))
summary_stats_size_2017

#####################################
# Test for normality with histogram and QQ-plot with new dataframe filtered for 2017 only.

size_2017 <- size_tidier %>%
  filter(YEAR == 2017)

# Loaded 1668 obs of 3 variables.

size_2017_hist <- ggplot(size_2017, aes(SIZE)) +
  geom_histogram(bins = 23) # Bins = 2*n^(1/3) = 23 bins; n = ~1500
size_2017_hist

size_2017_qq <- ggplot(size_2017, aes(sample = SIZE)) +
  geom_qq()
size_2017_qq

# Data appears normally distributed.
# > 2 samples
# n > 30

```

**Table 1. Summarized lobster carapace length at five sites in 2017.** Median, maximum, and mean lobster carapace length (mm) for sites AQUE, CARP, IVEE, MOHK, and NAPL in Santa Barbara County in 2017 (n = 1,668). Data were collected every two to four weeks from October to March by the Santa Barbara Coastal Long Term Ecological Research Project (SBC LTER).
```{r, echo = FALSE}
### 2. Compare mean lobster size across five sites in 2017
# Summary Statistics Table

summary_table <- kable(summary_stats_size_2017,
                       col.names = c("Site","Median","Max","Mean","SD","n"), 
                       align = "c") %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = FALSE) %>%
  add_header_above(c(" ","Lobster Carapace Length (mm)" = 5))
  
summary_table

```


```{r, echo = FALSE}
### 2. Compare mean lobster size across five sites in 2017.

####################################
# Hypothesis Test

# Question: Is there a difference in lobster carapace size between sites in 2017?

# H0: There is no difference in carapace size between sites in 2017.
# HA: At least two sites differ in carapace size in 2017.

# This sounds like an ANOVA!

size_2017_anova <- aov(SIZE ~ SITE, data = size_2017)
summary(size_2017_anova)
  
# There is a significant difference. How are they different?

###################################
# Tukey HSD

post_hoc_size_2017 <- TukeyHSD(size_2017_anova)
post_hoc_size_2017

# At first glance, the two following pairings are significantly different at alpha = 0.05.
# NAPL-CARP  4.0023556  0.36042398 7.644287 0.0228728
# NAPL-IVEE  4.7799976  1.09751057 8.462485 0.0037001

# NAPL-MOHK  4.2321429 -0.08607271 8.550358 0.0579286 is not significant.

# What is in-line referencing for AVONA?

```

Lobster carapace length significantly differs in at least two sites in 2017 (F(4,1663) = 3.42, $p$ = 0.0085, $\alpha$ = 0.05).

```{r, include = FALSE}
### 2. Compare mean lobster size across five sites in 2017

###################################
# ANOVA boxplot

boxplot_anova_size_2017 <- ggplot(size_2017, aes(x = SITE, y = SIZE)) +
  geom_boxplot() +
  xlab("\nSite") +
  ylab("Lobster Carapace Length (mm)\n") +
  theme_classic()
boxplot_anova_size_2017

```

```{r ANOVA_table, echo = FALSE, results = 'asis', message = FALSE}

table <- xtable(size_2017_anova, caption = 'Lobster carapace size by site ANOVA results summary.')
print(table, comment = FALSE, caption.placement = "top")

# Attempted an ANOVA summary table. It didn't work.

```

```{r, echo = FALSE, results = "asis"}
### 2. Compare mean lobster size across five sites in 2017

###################################
# Make column graph of mean carapace size w/ SD error bars

size_2017_graph <- ggplot(summary_stats_size_2017, aes(x = SITE, y = mean)) +
  geom_col(width = 0.5) +
  geom_errorbar(aes(ymax = mean + sd, ymin = mean - sd), width = 0.1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) + # Sets y-axis on x-axis line and adjusts scale.
  xlab("\nSite") +
  ylab("Mean Lobster Carapace Length (mm)\n") +
  annotate("text", x = 5, y = 90, label = "*") # Annotates graph.

size_2017_graph

```

**Figure 1. Lobster carapace length for five sites in 2017.** Mean lobster carapace length (mm) for sites AQUE (n = 67), CARP (n = 705), IVEE (n = 606), MOHK (n = 178), and NAPL (n = 112) in Santa Barbara County in 2017. Error bars indicate +/- 1 standard deviation. *Asterisk or letters indicate values that do/do not differ significantly* (by one-way ANOVA with Tukey's HSD; F(4,1663) = 3.42, $p$ = 0.0085) with $\alpha$ = 0.05 for all post-hoc pairwise comparison.


### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
```{r}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# MPA = NAPL, IVEE; non-MPA = AQUE, CARP, MOHK
# Summary Statistics
# Tests for normality
# Hypothesis Test

# Question 1: At MPA sites, how do lobster sizes in 2012 and 2017 compare?

# Question 2: At non-MPA sites, how do lobster sizes in 2012 and 2017 compare?

```


### 4. Proportions of "legal" lobsters at 5 sites in 2017
```{r}
### 4. Proportions of "legal" lobsters at 5 sites in 2017
# Legal minimum carapace size is 82.6 mm
# Chi-square test

# Question 1: What proportion of observed lobsters at each site are above the legal minumum?

ivprop <-size_2017 %>%
  filter(SITE == "IVEE")
prop(ivprop, SIZE > 82.6)

naprop <-size_2017 %>%
  filter(SITE == "NAPL")
prop(naprop, SIZE > 82.6)

aqprop <-size_2017 %>%
  filter(SITE == "AQUE")
prop(aqprop, SIZE > 82.6)

caprop <-size_2017 %>%
  filter(SITE == "CARP")
prop(caprop, SIZE > 82.6)

moprop <-size_2017 %>%
  filter(SITE == "MOHK")
prop(moprop, SIZE > 82.6)

# Question 2: Does that proportion differ significantly across 5 sites?

# H0: There is no notable difference between the proportion of lobsters above the legal size limit between the five sites. 
# HA: There is a notable difference between the proportion of lobsters above the legal size limit between the five sites.

chisq.test(c(.2145, .3304, .2388, .2539, .1348))


```








