---
title: "LobsterReport"
author: "Anna PerezWelter and Jamie K. Miller"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
### Install Packages

library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(pwr)
library(effsize)
library(ggplot2)
library(tidyr) # This package is to convert to tidy format with spread() function.
library(vcdExtra) # Perhaps this one will do it.
library(dplyr) # For summary stats?
library(sjstats) # For chi-square
library(ggsignif) # To add significance brackets
library(xtable) # For ANOVA table
library(RColorBrewer)
library(ggpubr)
library(car)
library(onewaytests)
```

```{r, message=FALSE, include = FALSE}
### Read in Data and Data Source

size <- read_csv("lobster_size_abundance.csv")

# Loaded 3265 obs of 8 variables.

traps <- read_csv("lobster_traps.csv")

# Loaded 5741 obs of 10 variables.

###############################

# Data Source: Reed, D. . 2017. SBC LTER: Reef: Abundance, size and fishing effort for California
# Spiny Lobster (Panulirus interruptus), ongoing since 2012. Santa Barbara Coastal Long Term Ecological
# Research Project. doi:10.6073/pasta/81ce20b29614ec99d85d54907eaa3e8e

```

 
```{r, message = FALSE, include = FALSE}
# Preliminary Data Exploration: Lobster counts at all five locations from 2012 to 2017. 

### Lobster Abundance Data Formating

# Filter to exclude rows where the lobster count was zero. Only show columns year, site, size, and count.

size_tidy <- size %>%
  select(YEAR, SITE, SIZE, COUNT) %>%
  filter(COUNT != 0)

# Loaded 2878 obs of 4 variables.

######################

# Convert file 'size' to tidy format

size_tidier <- size_tidy %>%
  as.data.frame() %>%
  expand.dft(freq = "COUNT")

# Loaded 4554 obs of 3 variables.

# Lobster carapace length and counts are now in tidy format. Use 'size_tidier'.

size_tidier
```

### 1. Lobster abundance and fishing pressure (2012-2017)
```{r, echo = FALSE, include = FALSE}
# Data Exploration: Lobster counts at all five locations from 2012 to 2017. 

### 1. Lobster abundance and fishing pressure (2012-2017)

# 1a. Summarize  trap data in a table grouped by Year and Site, filtered by 5 sites.
# Trap abundance bar graph to show fishing pressure per year at each site.

traps_summary <- traps %>%
  select(YEAR, SITE, TRAPS) %>%
  filter(SITE == "AQUE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "IVEE" | SITE == "CARP") %>%
  group_by(YEAR, SITE) %>%
  summarize(count = length(TRAPS))

# Loaded 30 obs of 3 variables summary table.

trap_graph <- ggplot(traps_summary, aes(x = YEAR, y = count)) +
                       geom_bar(position = position_dodge(), stat = "identity") +
                       facet_wrap(~SITE) +
  theme_classic()
trap_graph

```

```{r, echo = FALSE, include = FALSE}
### 1. Lobster abundance and fishing pressure (2012-2017)

# 1b. Summarize lobster data in a table grouped by Year and Site, filtered by 5 sites.
# Lobster abundance bar graph

lobster_summary <- size_tidier %>%
  filter(SITE == "AQUE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "IVEE" | SITE == "CARP") %>%
  group_by(YEAR, SITE) %>%
  summarize(count = length(SIZE))

lobster_graph <- ggplot(lobster_summary, aes(x = YEAR, y = count)) +
                      geom_bar(position = position_dodge(), stat = "identity") +
                      facet_wrap(~SITE, scale = "free") +
  theme_classic()
lobster_graph
```

```{r, echo = FALSE}
### 1. Lobster abundance and fishing pressure (2012-2017)
# Trapping Pressure graph

trap_graph_2 <- ggplot(traps_summary, aes(x = YEAR, y = count)) +
                       geom_bar(position = position_dodge(), stat = "identity", aes(fill = SITE)) +
  scale_fill_manual(
values = c("grey75", "grey60","grey40", "grey30", "grey20"),
limits = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"), breaks =c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"),
name = "Site", labels = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL")) +
  theme_classic() +
  ylab("Number of Traps\n") +
  xlab("\nYear") +
  ggtitle("Trapping Pressure at Each Site by Year\n") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(2012,2013,2014,2015,2016,2017)) +
  scale_y_continuous(expand = c(0,0))

trap_graph_2


```

**Figure 1. Lobster trapping pressure at five sites from 2012 to 2017.** Total number of lobster traps at each site (AQUE, CARP, IVEE, MOHK, and NAPL) in Santa Barbara County from 2012 to 2017. Data were collected every two to four weeks from October to March by the Santa Barbara Coastal Long Term Ecological Research Project (SBC LTER).

Relative lobster trapping pressure was consistent each year with the highest trapping pressure at IVEE and the lowest at NAPL for each year (Figure 1). Trapping pressure from all sites increased from 2012 to 2013, then remained constant in 2014. Pressure decreased in 2015 then increased again in 2016. Trapping pressure at all sites greatly decreased to its lowest levels overall in 2017.


```{r, echo = FALSE}
### 1. Lobster abundance and fishing pressure (2012-2017)
# Lobster Abundance graph

lobster_graph_2 <- ggplot(lobster_summary, aes(x = YEAR, y = count)) +
                      geom_bar(position = position_dodge(), 
                               stat = "identity", aes(fill = SITE)) +
  scale_fill_manual(
values = c("grey75", "grey60","grey40", "grey30", "grey20"),
limits = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"), breaks =c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"),
name = "Site", labels = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL")) +
  theme_classic() +
  ylab("Number of Lobsters\n") +
  xlab("\nYear") +
  ggtitle("Lobster Abundance at Each Site by Year") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(2012,2013,2014,2015,2016,2017)) +
  scale_y_continuous(expand = c(0,0))
    
lobster_graph_2

```

**Figure 2. Lobster abundance at five sites from 2012 to 2017.** Total number of lobsters observed at each site (AQUE, CARP, IVEE, MOHK, and NAPL) in Santa Barbara County from 2012 to 2017. Data were collected every two to four weeks from October to March by the Santa Barbara Coastal Long Term Ecological Research Project (SBC LTER).

Lobster abundance was relatively low from 2012 to 2014 (Figure 2). Abundance increased at IVEE, MOHK, and NAPL in 2015 when trapping pressure decreased. Abundance decreased at all sites except for CARP in 2016. Abundance drastically increased at CARP and IVEE in 2017 while the others remained relatively constant.

### 2. Compare mean lobster size across five sites in 2017
```{r, include = FALSE}
### 2. Compare mean lobster size across five sites in 2017
# Summary Statistics
# Tests for normality
# Hypothesis Test

#####################################
# Summary Statistics
# Create a summary table, grouped by site, that includes median, maximum, mean, sd, and sample size values.
# Round values to 2 decimal points.

summary_stats_size_2017 <- size_tidier %>%
  filter(YEAR == 2017) %>%  
  group_by(SITE) %>%
  summarize(median = round(median(SIZE),2), 
            max = max(SIZE),
            mean = round(mean(SIZE),1),
            sd = round(sd(SIZE),1),
            n = length(SIZE))
summary_stats_size_2017

#####################################
# Test for normality with histogram and QQ-plot with new dataframe filtered for 2017 only.

size_2017 <- size_tidier %>%
  filter(YEAR == 2017)

# Loaded 1668 obs of 3 variables.

size_2017_hist <- ggplot(size_2017, aes(SIZE)) +
  geom_histogram(bins = 23) # Bins = 2*n^(1/3) = 23 bins; n = ~1500
size_2017_hist

size_2017_qq <- ggplot(size_2017, aes(sample = SIZE)) +
  geom_qq()
size_2017_qq

# Data appears normally distributed.
# > 2 samples
# n > 30

```

**Table 1. Summarized lobster carapace length at five sites in 2017.** Median, maximum, and mean lobster carapace length (mm) for Santa Barbara County sites (AQUE, CARP, IVEE, MOHK, and NAPL) in 2017 (n = 1668). Data were collected every two to four weeks from October to March by the Santa Barbara Coastal Long Term Ecological Research Project (SBC LTER).
```{r, echo = FALSE}
### 2. Compare mean lobster size across five sites in 2017
# Summary Statistics Table

summary_table <- kable(summary_stats_size_2017,
                       col.names = c("Site","Median","Max","Mean","SD","n"), 
                       align = "c") %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = FALSE) %>%
  add_header_above(c(" ","Lobster Carapace Length (mm)" = 5))
  
summary_table

```

```{r, include = FALSE}
## DO LEVENE'S TEST HERE

variances <- size_2017 %>% 
  group_by(SITE) %>% 
  summarize(
    mean = mean(SIZE),
    sd = sd(SIZE),
    variance = var(SIZE)
  )

variances # Definitely are not close (also see that this lines up with Levene's test)

size_2017_levene <- leveneTest(SIZE ~ SITE, data = size_2017)

size_2017_levene # Variances are significantly different


```



```{r, echo = FALSE, include = FALSE}
### 2. Compare mean lobster size across five sites in 2017.

####################################
# Hypothesis Test

# Question: Is there a difference in lobster carapace size between sites in 2017?

# H0: There is no difference in carapace size between sites in 2017.
# HA: At least two sites differ in carapace size in 2017.

# This sounds like an ANOVA!

size_2017_anova <- aov(SIZE ~ SITE, data = size_2017)
summary(size_2017_anova)
  
# There is a significant difference. How are they different?

###################################
# Tukey HSD

post_hoc_size_2017 <- TukeyHSD(size_2017_anova)
post_hoc_size_2017

# At first glance, the two following pairings are significantly different at alpha = 0.05.
# NAPL-CARP  4.0023556  0.36042398 7.644287 0.0228728
# NAPL-IVEE  4.7799976  1.09751057 8.462485 0.0037001

# NAPL-MOHK  4.2321429 -0.08607271 8.550358 0.0579286 is not significant.

# What is in-line referencing for AVONA?

```
The total number of lobsters observed in 2017 was lowest at AQUE (n = 67) and highest at CARP (n = 705) and IVEE (n = 606) (Table 1).The largest lobster with a carapace length of 150 mm was observed at IVEE. Lobster carapace length significantly differed in at least two sites in 2017 (one-way ANOVA, F(4,1663) = 3.42, $p$ = 0.0085, $\alpha$ = 0.05). Post-hoc analysis with Tukey's HSD found that lobsters at the NAPL site had the highest mean carapace length of 76.2 +/- 11.4 mm (mean +/- sd, n = 112), and differed significantly from those at CARP (72.2 +/- 13.2 mm (mean +/- sd), n = 705, pairwise p = 0.023) and IVEE (71.5 +/- 14.3 mm (mean +/- sd), n = 606, pairwise p = 0.004) (Figure 3). Carapace length was not significantly different between any of the other sites.

```{r, include = FALSE}
### 2. Compare mean lobster size across five sites in 2017

###################################
# ANOVA boxplot

boxplot_anova_size_2017 <- ggplot(size_2017, aes(x = SITE, y = SIZE)) +
  geom_boxplot() +
  xlab("\nSite") +
  ylab("Lobster Carapace Length (mm)\n") +
  theme_classic()
boxplot_anova_size_2017

# I think the column graph is a better way to show this.

```

```{r ANOVA_table, echo = FALSE, include = FALSE, message = FALSE}

table <- xtable(size_2017_anova, caption = 'Lobster carapace size by site ANOVA results summary.')
print(table, comment = FALSE, caption.placement = "top")

# Attempted an ANOVA summary table. It didn't work.

```

```{r, echo = FALSE, results = "asis"}
### 2. Compare mean lobster size across five sites in 2017

###################################
# Make column graph of mean carapace size w/ SD error bars

size_2017_graph <- ggplot(summary_stats_size_2017, aes(x = SITE, y = mean)) +
  geom_col(width = 0.5) +
  geom_errorbar(aes(ymax = mean + sd, ymin = mean - sd), width = 0.1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) + # Sets y-axis on x-axis line and adjusts scale.
  xlab("\nSite") +
  ylab("Mean Lobster Carapace Length (mm)\n") +
  ggtitle("Lobster Carapace Length (mm) by Site") +
  theme(plot.title = element_text(hjust = 0.5)) +
  annotate("text", x = 5, y = 91, label = "a") + # Annotates graph.
  annotate("text", x = 2:3, y = 89, label = "b")
  

# geom_signif(comparisons = list(c("NAPL", "IVEE")),
#               map_signif_level = FALSE, textsize=2) +
#  ylim(NA, 95) +
#  geom_signif(comparisons = list(c("NAPL", "CARP")),
#               map_signif_level = FALSE, textsize=2) +
#  ylim(NA, 100)
# Add pairwise comparisons p-value. None of it worked.

size_2017_graph

```

**Figure 3. Lobster carapace length for five sites in 2017.** Mean lobster carapace length (mm) for sites AQUE (n = 67), CARP (n = 705), IVEE (n = 606), MOHK (n = 178), and NAPL (n = 112) in Santa Barbara County in 2017. Error bars indicate +/- 1 standard deviation. Letters indicate that NAPL (a) differed significantly from CARP (b) and IVEE (b) (one-way ANOVA with Tukey's HSD; F(4,1663) = 3.42, $p$ = 0.0085) with $\alpha$ = 0.05 for all post-hoc pairwise comparisons.


### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
```{r, include=FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# MPA = NAPL, IVEE; non-MPA = AQUE, CARP, MOHK
# Summary Statistics
# Tests for normality
# Hypothesis Test

# Question 1: At MPA sites, how do lobster sizes in 2012 and 2017 compare?
# Question 2: At non-MPA sites, how do lobster sizes in 2012 and 2017 compare?

mpa_size <- size_tidier %>%
  mutate(MPA = case_when(SITE == "NAPL" ~ "MPA", 
                         SITE == "IVEE" ~ "MPA",
                         SITE == "CARP" ~ "non-MPA",
                         SITE == "MOHK" ~ "non-MPA",
                         SITE == "AQUE" ~ "non-MPA")) %>%
  filter(YEAR == "2012" | YEAR == "2017")

mpa_size


```

```{r, include = FALSE}
## DO LEVENE'S TEST HERE

variances_mpa <- mpa_size %>% 
  group_by(SITE) %>% 
  summarize(
    mean = mean(SIZE),
    sd = sd(SIZE),
    variance = var(SIZE)
  )

variances_mpa # Definitely are not close (also see that this lines up with Levene's test)

mpa_levene <- leveneTest(SIZE ~ SITE, data = mpa_size)

mpa_levene # Variances are significantly different

# tests are identical to the one runs for size_2017. same data.

```


```{r, echo = FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
#### Summary Stats

summary_stats_mpa <- mpa_size %>%
  group_by(MPA, YEAR) %>%
  summarize(median = round(median(SIZE),2), 
            max = max(SIZE),
            mean = round(mean(SIZE),1),
            sd = round(sd(SIZE),1),
            n = length(SIZE))
summary_stats_mpa
```

```{r, include = FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# Graph

mpa_graph <- ggplot(summary_stats_mpa, aes(x = YEAR, y = mean)) +
  geom_col(position = position_dodge(), stat = "identity", aes(fill = MPA)) +
  scale_fill_manual(
values = c("grey60","grey20"),
limits = c("MPA","non-MPA"), breaks =c("MPA","non-MPA"),
name = "Year", labels = c("MPA","non-MPA")) +
  theme_classic() +
  ylab("Mean Lobster Carapace Length (mm)\n") +
  xlab("\nYear") +
  ggtitle("Lobster Size by Year at MPA and non-MPA sites") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(breaks = c(2012,2017)) +
  scale_y_continuous(expand = c(0,0))

mpa_graph

# This does not appear useful. I will make a table instead.

```

**Table 2. Summarized lobster carapace length at MPA and non-MPA sites in 2012 and 2017.** Median, maximum, and mean lobster carapace length (mm) for Santa Barbara County MPA (IVEE and NAPL) and non-MPA sites (AQUE, CARP, and MOHK) in 2012 and 2017 (n = 1899). Data were collected every two to four weeks from October to March by the Santa Barbara Coastal Long Term Ecological Research Project (SBC LTER).

```{r, echo = FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# Summary Statistics Table

summary_table_mpa <- kable(summary_stats_mpa,
                       col.names = c("MPA Status","Year","Median","Max","Mean","SD","n"), 
                       align = "c") %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = FALSE) %>%
  add_header_above(c("","","Lobster Carapace Length (mm)" = 5))

summary_table_mpa

#  group_rows("MPA",1,2) %>%
#  group_rows("Non-MPA",3,4)

```
Lobster carapace length and individual abundance increased at MPA sites from 2012 (67.4 +/- 12.2 mm (mean +/- sd), n = 32) to 2017 (72.2 +/- 14.0 mm (mean +/- sd), n = 718). At non-MPA sites, carapace size decreased and abundance increased from 2012 (74.9 +/- 12.4 mm (mean +/- sd), n = 199) to 2017 (72.3 +/- 12.5 mm (mean +/- sd, n = 32) (Table 2). The increase in lobster abundance from 2012 to 2017 represents at 2144% and 377% increase at MPA and non-MAP sites, respectively. 



```{r, include = FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# Test for normality with histogram and QQ-plot with new dataframe filtered for 2012 and 2017.

mpa_hist <- ggplot(mpa_size, aes(SIZE)) +
  geom_histogram(bins = 23) # Bins = 2*n^(1/3) = 23 bins; n = ~1500
mpa_hist

mpa_qq <- ggplot(mpa_size, aes(sample = SIZE)) +
  geom_qq()
mpa_qq

# yup, it's normally distributed.

```

```{r, include = FALSE}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# F test for equal variances

mpa_ftest <- mpa_size %>%
  var.test(YEAR ~ MPA, data = .)
mpa_ftest

# Variances are not equal.

```


```{r}
### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# Hypothesis test

#H0: At MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At MPA sites, there is a difference in carapace size between 2012 and 2017.

#H0: At non-MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At non-MPA sites, there is a difference in carapace size between 2012 and 2017.


mpa_ttest <- t.test(mpa_size$YEAR, mpa_size$SIZE, conf.level=0.95)
mpa_ttest


#  alternative = "greater"

```
A paired two-tailed, two-sample t-test shows that there is a significant difference in carapace size between MPA and non-MPA sites between 2012 and 2017 (t(1898) = -6387.9, p < 0.0001, $\alpha$ = 0.05).


```{r}
#H0: At MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At MPA sites, there is a difference in carapace size between 2012 and 2017.

mpa_only <- mpa_size %>%
  filter(MPA == "MPA")

mpa_only_ttest <- t.test(mpa_only$YEAR, mpa_only$SIZE, conf.level=0.95)
mpa_only_ttest


```

```{r}
#H0: At non-MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At non-MPA sites, there is a difference in carapace size between 2012 and 2017.

non_mpa_only <- mpa_size %>%
  filter(MPA == "non-MPA")

non_mpa_only_ttest <- t.test(non_mpa_only$YEAR, non_mpa_only$SIZE, conf.level=0.95)
non_mpa_only_ttest


```

#### Now let's try this with directionalisty

```{r}
### Directional ###

### 3. Change in lobster size at MPA and non-MPA sites between 2012 and 2017
# Hypothesis test

#H0: At MPA sites, carapace size is NOT greater in 2017 than 2012.
#HA: At MPA sites, carapace size is greater in 2017 than 2012.

#H0: At non-MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At non-MPA sites, there is a difference in carapace size between 2012 and 2017.


mpa_ttest_greater <- t.test(mpa_size$YEAR, mpa_size$SIZE, conf.level=0.95, alternative = "greater")
mpa_ttest_greater


#  alternative = "greater"

```


```{r}
### Directional ###

#H0: At MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At MPA sites, there is a difference in carapace size between 2012 and 2017.

mpa_only_ttest_greater <- t.test(mpa_only$YEAR, mpa_only$SIZE, conf.level=0.95, alternative = "greater")
mpa_only_ttest_greater


```

```{r}
### Directional ###

#H0: At non-MPA sites, there is no difference in carapace size between 2012 and 2017.
#HA: At non-MPA sites, there is a difference in carapace size between 2012 and 2017.

non_mpa_only_ttest_greater <- t.test(non_mpa_only$YEAR, non_mpa_only$SIZE, conf.level=0.95)
non_mpa_only_ttest_greater


```



### 4. Proportions of "legal" lobsters at 5 sites in 2017
```{r, include = FALSE}
### 4. Proportions of "legal" lobsters at 5 sites in 2017
# Legal minimum carapace size is 82.6 mm
# Chi-square test

# Question 1: What proportion of observed lobsters at each site are above the legal minumum?

ivprop <-size_2017 %>%
  filter(SITE == "IVEE")
prop(ivprop, SIZE > 82.6)

naprop <-size_2017 %>%
  filter(SITE == "NAPL")
prop(naprop, SIZE > 82.6)

aqprop <-size_2017 %>%
  filter(SITE == "AQUE")
prop(aqprop, SIZE > 82.6)

caprop <-size_2017 %>%
  filter(SITE == "CARP")
prop(caprop, SIZE > 82.6)

moprop <-size_2017 %>%
  filter(SITE == "MOHK")
prop(moprop, SIZE > 82.6)

# Question 2: Does that proportion differ significantly across 5 sites?

# H0: There is no notable difference between the proportion of lobsters above the legal size limit between the five sites. 
# HA: There is a notable difference between the proportion of lobsters above the legal size limit between the five sites.

chisq.test(c(.2145, .3304, .2388, .2539, .1348))

#Given that the p-value is high (0.99), there is no significant difference between the different sites in terms of proportions of lobsters observed above the legal size limit. 
```

```{r, include = FALSE}
# Chi Square Analysis

# creat new data frame assigning legal and not legal sizes

lobster_legal <- size_2017 %>%
  mutate(size=ifelse(SIZE <= 82.6, "Not Legal", "Legal"))

lobster_legal

lobster_legal_table <- lobster_legal %>%
  count(SITE, size) %>%
  spread(size, n) %>%
  select(-SITE)

lobster_legal_table

```
```{r}
# Chi Square test

chi_test = chisq.test(lobster_legal_table, simulate.p.value = TRUE)
chi_test


```
 There is an association between size and MPA site designation. x^2^(4) = 18.5, p = 0.0009995


### Discussion

There is a vast difference in sample sites between sites. AQUE n = 67 vs. CARP n = 705. Greater abundance at CARP and AQUE compared to other sites. 



### Conclusions

-What we will likely find is that MPA sites will have larger and more lonsters than non-MPA sites.
-Lobster numbers increase after MPAs put in place
-as trapping decrease, lobster numbers and sizes increase.
-greater proportion of "legal size" lobsters at MPS site.
-we'll need to be careful with these statements because we haven't done direction tests with some of them yet. We have just shown that there is a significant difference.


